The illusory promise of the Aligned Rank Transform

### 2025-12-10 sandbox.qmd
starting new revisions

::: {.callout-important appearance="simple"}
## Under Review {.unnumbered}
This paper is [under review](https://www.journalovi.org/under-review.html) on the experimental track of
the [Journal of Visualization and Interaction](https://www.journalovi.org/). See the 
[reviewing process](https://github.com/journalovi/2024-tsandilas-ranktransforms/issues).
:::

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Source code for reading data from experimental results and for plotting
source("dataReaders.R")
source("plotting.R")
source("plotlying.R")
source("effects_plot.R")
source("interactions_plot.R")
```

@@

>>>>

@@

@@

::: {#fig-ratio-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
library(dplyr)
library(tidyverse)
source("utils-data-reading.R")
source("utils-plotlying.R")
```
:::

::: {#fig-power-main-1}
<div id="plot-power-1.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Power"
distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

data <- read_data(prefix, alpha = .05, effectType = 3, distributions)
df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of main effect", var = "rateX1", xvar = "effectX1", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-1.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX1,rateX1)  %>% group_by(design,family,effectX1) %>% mutate(rank = rank(rateX1))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX1", xvar = "effectX1", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-1.2").classList.add("hidden"); }); </script>

<button id="btn1" style="background-color: #f0f0f0; border: 1px solid #ccc; color: #333; font-size: 0.9em;
    padding: 4px 10px; border-radius: 6px; cursor: pointer; float: right;"
  onclick="const plot = document.getElementById('plot-power-1.1');
  plot.classList.toggle('hidden');
  document.getElementById('plot-power-1.2').classList.toggle('hidden');
  btn1.innerText = plot.classList.contains('hidden') ? 'show percent' : 'show ranking';
">
  show ranking
</button>

Power ($\alpha = .05$) for detecting the **main effect of $X_1$** as a function of its magnitude $a_1$, where $n=20$.
:::

@fig-power-main-2 presents our results for $X_2$. Given the different number of levels for this factor, we now assess a different range of power for each design. Nevertheless, we observe similar patterns. INT stands out as the most powerful method. Although ART surpasses PAR under the log-normal and exponential distributions, it does not demonstrate any other notable advantages compared to the other methods.

::: {#fig-power-main-2}
<div id="plot-power-2.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- read_data(prefix, alpha=.05, effectType = 4, distributions) # CHANGE n TO 20

df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-2.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX2,rateX2)  %>% group_by(design,family,effectX2) %>% mutate(rank = rank(rateX2))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshape_by_design(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX2", xvar = "effectX2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-2.2").classList.add("hidden"); }); </script>

<button id="btn2" style="background-color: #f0f0f0; border: 1px solid #ccc; color: #333; font-size: 0.9em;
    padding: 4px 10px; border-radius: 6px; cursor: pointer; float: right;"
  onclick="const plot = document.getElementById('plot-power-2.1');
  plot.classList.toggle('hidden');
  document.getElementById('plot-power-2.2').classList.toggle('hidden');
  btn2.innerText = plot.classList.contains('hidden') ? 'show percent' : 'show ranking';
">
  show ranking
</button>

Power ($\alpha = .05$) for detecting the **main effect of $X_2$** as a function of its magnitude $a_2$, where $n=20$. 
:::

**Interaction effects**. We also vary the magnitude of the interaction effect $X_1 \times X_2$ by manipulating the parameter $a_{12}$ across the range of $0.5$ to $2.0$. We then measure the power to detect this interaction effect. Our results are summarized in @fig-power-interaction, aligning with findings for main effects. ART's relative advantage diminishes later under the binomial and ordinal distributions. Once again, the method's inflated Type I error rates could account for this observed trend.

::: {#fig-power-interaction}
<div id="plot-power-3.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- read_data(prefix, alpha=.05, effectType = 5, distributions)

df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of interaction effect", var = "rateX1X2", xvar = "effectX1X2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-3.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX1X2,rateX1X2)  %>% group_by(design,family,effectX1X2) %>% mutate(rank = rank(rateX1X2))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshape_by_design(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of interaction effect", var = "rank", hovervar = "rateX1X2", xvar = "effectX1X2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-3.2").classList.add("hidden"); }); </script>

<button id="btn3" style="background-color: #f0f0f0; border: 1px solid #ccc; color: #333; font-size: 0.9em;
    padding: 4px 10px; border-radius: 6px; cursor: pointer; float: right;"
  onclick="const plot = document.getElementById('plot-power-3.1');
  plot.classList.toggle('hidden');
  document.getElementById('plot-power-3.2').classList.toggle('hidden');
  btn3.innerText = plot.classList.contains('hidden') ? 'show percent' : 'show ranking';
">
  show ranking
</button>

Power ($\alpha = .05$) for detecting the **interaction effect $X_1 \times X_2$** as a function of its magnitude $a_{12}$, where $n=20$.
:::

### 2025-12-10 text/60-Results-RatioScales.qmd
starting new revisions

::: {#fig-ratio-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
library(dplyr)
library(tidyverse)
source("dataReaders.R")
source("plotlying.R")

prefix <- "1_test_4x3_Ratio"
alpha <- .05
distributions <- c("norm", "lnorm", "exp", "cauchy", "poisson", "binom")
dnames <- c("Normal", "Log-normal", "Exponential", "Cauchy", "Poisson", "Binomial")
df <- readlyData(prefix, alpha, 1, distributions, dnames)
plotlyError(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 64)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$
:::

@@

::: {#fig-ratio-contrasts}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "1_test_4x3_Contrasts"

df <- readlyData(prefix, alpha, 1, distributions, dnames)
plotlyError(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 52)
```
Average Type I error rates ($\alpha = .05$) for **contrasts on factor $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

::: {#fig-ratio-interaction-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "1_test_4x3_Ratio"
df <- readlyData(prefix, alpha, 1, distributions, dnames)

plotlyError(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 52)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

>>>>

::: {#fig-ratio-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
library(dplyr)
library(tidyverse)
source("utils-data-reading.R")
source("utils-plotlying.R")

# To remote those: 
source("dataReaders.R")
source("plotlying.R")

prefix <- "Type_I_4x3_ratio"
alpha <- .05
distributions <- c("norm", "lnorm", "exp", "cauchy", "poisson", "binom")
dnames <- c("Normal", "Log-normal", "Exponential", "Cauchy", "Poisson", "Binomial")
df <- readly_data(prefix, alpha, 1, distributions, dnames)
plotly_error(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 102)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$
:::

@@

::: {#fig-ratio-contrasts}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_4x3_ratio_contrasts"

df <- readly_data(prefix, alpha, 1, distributions, dnames)
plotly_error(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 101)
```
Average Type I error rates ($\alpha = .05$) for **contrasts on factor $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

::: {#fig-ratio-interaction-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_4x3_ratio"
df <- readly_data(prefix, alpha, 1, distributions, dnames)

plotly_error(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 100)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

**Analysis for large samples.** Let us further explore ART's error rates when sample sizes become larger.

::: {#fig-ratio-large-samples}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_4x3_ratio_large_samples"

distributions <- c("norm", "lnorm", "exp", "cauchy", "poisson", "binom")
dnames <- c("Normal", "Log-normal", "Exponential", "Cauchy", "Poisson", "Binomial")

df <- readly_data_1(prefix, alpha, 1, distributions, dnames)
plotly_error_by_effect_1(df, xlab = "n", max = 86)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** and the **interaction** $X_1 \times X_2$ as a function of the size $n$ of the sample. The effect on $X_1$ is non-null, where we set $a_1 = 1$.
:::

### 2025-12-10 text/61-Results-OrdinalScales.qmd
starting new revisions

::: {#fig-ordinal-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "2_test_4x3_Ordinal"

distributions <- c("likert5", "likert5B", "likert7", "likert7B", "likert11", "likert11B")
dnames <- c("5 - equidistant", "5 - flexible", "7 - equidistant", "7 - flexible", "11 - equidistant", "11 - flexible")
df <- readlyData(prefix, alpha, 1, distributions, dnames)

plotlyError(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 52)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$
:::

@@

plotlyError(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 45)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

::: {#fig-ordinal-large-samples}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "2_test_4x3_Ordinal_sample_size"

distributions <- c("likert5", "likert5B", "likert7", "likert7B", "likert11", "likert11B")
dnames <- c("5 - equidistant", "5 - flexible", "7 - equidistant", "7 - flexible", "11 - equidistant", "11 - flexible")

df <- readlyData1(prefix, alpha, 0, distributions, dnames)
plotlyErrorByEffect(df, xlab = "n", max = 100)
```
Type I error rates ($\alpha = .05$) as a function of the size $n$ of the sample, where all population effects are null.
:::

We will observe similar trends if we test other discrete distributions, such as binomial distributions. These results confirm that ART is inappropriate for discrete data.

>>>>

::: {#fig-ordinal-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_ordinal"

distributions <- c("likert_5", "likert_5_flex", "likert_7", "likert_7_flex", "likert_11", "likert_11_flex")
dnames <- c("5 - equidistant", "5 - flexible", "7 - equidistant", "7 - flexible", "11 - equidistant", "11 - flexible")
df <- readly_data(prefix, alpha, 1, distributions, dnames)

plotly_error(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 60)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$
:::

@@

plotly_error(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 50)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ 
:::

@@

::: {#fig-ordinal-large-samples}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_4x3_ordinal_large_samples"

df <- readly_data_1(prefix, alpha, 0, distributions, dnames)
plotly_error_by_effect_2(df, xlab = "n", max = 100)
```
Type I error rates ($\alpha = .05$) as a function of the size $n$ of the sample, where all population effects are null.
:::

### 2025-12-10 text/62-Results-AcrossExpDesigns.qmd
starting new revisions

::: {#fig-designs-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "3_test-Designs"
alpha = 0.05

distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert5B")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

df <- readData(prefix, n = 20, alpha, effectType = 1, distributions)
df <- reshapeByDesign(df, dnames)

plotlyErrorByDesign(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 62)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$ ($n = 20$)
:::

We provide additional results for the between-subjects design in @fig-2x3-main, where we vary the effect of $X_2$ and measure Type I error rates on $X_1$. ART's error rates for the three discrete distributions appear higher than those observed in @fig-designs-main, indicating a potential dependence on the number of levels of the factors. Again, we observe a consistent trend where error rates in all discrete distributions increase with the sample size.

::: {#fig-2x3-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix2 <- "3_test-Designs_2x3"

df2x3 <- readlyData2(prefix2, alpha, effectType = 2, distributions, dnames)

plotlyError(df2x3, xlab = "magnitude of main effect", var = "rateX1", xvar = "effectX2", max = 62)
```
Additional results for the $2 \times 3$ between-subjects design, where we measure Type I error rates ($\alpha = .05$) for the **main effect of $X_1$.** We now vary the magnitude $a_2$ of the main effect of $X_2$.
:::

@@

::: {#fig-designs-interaction-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotlyErrorByDesign(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 62)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ ($n = 20$) 
:::

>>>>

::: {#fig-designs-main}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_designs"
alpha = 0.05

distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

df <- read_data(prefix, alpha, effectType = 1, distributions)
df <- reshape_by_design(df, dnames)

plotly_error_by_design(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX1", max = 101)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as a function of the magnitude $a_1$ of the main effect of $X_1$ ($n = 20$)
:::

@@

::: {#fig-designs-interaction-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotly_error_by_design(df, xlab = "magnitude of main effect", var = "rateX1X2", xvar = "effectX1", max = 101)
```
Type I error rates ($\alpha = .05$) for the **interaction** $X_1 \times X_2$ as a function of the magnitude $a_1$ of the main effect of $X_1$ ($n = 20$) 
:::

### 2025-12-10 text/63-Results-UnequalVariance.qmd
starting new revisions

::: {#fig-unequal-main-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "4_test_Unequal_Variances"
distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert5B")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

df <- readData(prefix, n = 20, alpha, effectType = 1, distributions)
df <- reshapeByDesign(df, dnames, effectvars = c("sd_ratio", "effectX1","effectX2","effectX1X2"))
plotlyErrorByDesign2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX1", xvar = "sd_ratio", max = 82, ytitle = 'Positives (%)')
```
The percentage of positives (i.e., rejecting the null hypothesis) for the **main effect of $X_1$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$). Depending on the hypothesis of interest, these percentages can be interpreted as Type I error rates ($\alpha = .05$).
:::

@@

::: {#fig-unequal-main-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotlyErrorByDesign2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX2", xvar = "sd_ratio", max = 52)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$)
:::

@@

::: {#fig-unequal-interaction}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotlyErrorByDesign2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX1X2", xvar = "sd_ratio", max = 52)
```
Type I error rates ($\alpha = .05$) for the **interaction effect $X_1 \times X_2$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$)
:::

>>>>

::: {#fig-unequal-main-1}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Type_I_heteroscedacity"
distributions = c("norm", "likert_5", "likert_5_flex", "likert_7", "likert_7_flex")
dnames = c("Normal", "Equidistant (5 levels)", "Flexible (5 levels)", "Equidistant (7 levels)", "Flexible (7 levels)")

df <- read_data(prefix, alpha = 0.05, effectType = 1, distributions)
df <- reshape_by_design(df, dnames, effectvars = c("sdratio", "effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX1", xvar = "sdratio", max = 41)
```
The percentage of positives (i.e., rejecting the null hypothesis) for the **main effect of $X_1$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$). Depending on the hypothesis of interest, these percentages can be interpreted as Type I error rates ($\alpha = .05$).
:::

@@

::: {#fig-unequal-main-2}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotly_error_by_design_2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX2", xvar = "sdratio", max = 41)
```
Type I error rates ($\alpha = .05$) for the **main effect of $X_2$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$)
:::

@@

::: {#fig-unequal-interaction}
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
plotly_error_by_design_2(df, xlab = "max ratio of standard deviations between levels of X1", var = "rateX1X2", xvar = "sdratio", max = 42)
```
Type I error rates ($\alpha = .05$) for the **interaction effect $X_1 \times X_2$** as the ratio of standard deviations $r_{sd}$ on $X_1$ increases ($n=20$)
:::

### 2025-12-10 text/64-Results-StatPower.qmd
starting new revisions

::: {#fig-power-main-1}
<div id="plot-power-1.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "5_test-Power"
distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert5B")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

data <- readData(prefix, n = 20, alpha = .05, effectType = 3, distributions)
df <- reshapeByDesign(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyErrorByDesign2(df, xlab = "magnitude of main effect", var = "rateX1", xvar = "effectX1", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-1.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,distr,effectX1,rateX1)  %>% group_by(design,distr,effectX1) %>% mutate(rank = rank(rateX1))
df <- as.data.frame(df) %>% reshapeByDesign(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyPowerByDesign(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX1", xvar = "effectX1", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-1.2").classList.add("hidden"); }); </script>

@@

::: {#fig-power-main-2}
<div id="plot-power-2.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- readData(prefix, n = 20, alpha, effectType = 4, distributions) # CHANGE n TO 20

df <- reshapeByDesign(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyErrorByDesign2(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-2.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,distr,effectX2,rateX2)  %>% group_by(design,distr,effectX2) %>% mutate(rank = rank(rateX2))
df <- as.data.frame(df) %>% reshapeByDesign(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshapeByDesign(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyPowerByDesign(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX2", xvar = "effectX2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-2.2").classList.add("hidden"); }); </script>

@@

::: {#fig-power-interaction}
<div id="plot-power-3.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- readData(prefix, n = 20, alpha, effectType = 5, distributions)

df <- reshapeByDesign(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyErrorByDesign2(df, xlab = "magnitude of interaction effect", var = "rateX1X2", xvar = "effectX1X2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-3.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,distr,effectX1X2,rateX1X2)  %>% group_by(design,distr,effectX1X2) %>% mutate(rank = rank(rateX1X2))
df <- as.data.frame(df) %>% reshapeByDesign(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshapeByDesign(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotlyPowerByDesign(df, xlab = "magnitude of interaction effect", var = "rank", hovervar = "rateX1X2", xvar = "effectX1X2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-3.2").classList.add("hidden"); }); </script>

>>>>

::: {#fig-power-main-1}
<div id="plot-power-1.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
prefix <- "Power"
distributions = c("norm", "lnorm", "exp", "poisson", "binom", "likert")
dnames = c("Normal", "Log-normal", "Exponential", "Poisson", "Binomial", "Ordinal (5 levels)")

data <- read_data(prefix, alpha = .05, effectType = 3, distributions)
df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of main effect", var = "rateX1", xvar = "effectX1", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-1.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX1,rateX1)  %>% group_by(design,family,effectX1) %>% mutate(rank = rank(rateX1))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX1", xvar = "effectX1", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-1.2").classList.add("hidden"); }); </script>

@@

::: {#fig-power-main-2}
<div id="plot-power-2.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- read_data(prefix, alpha=.05, effectType = 4, distributions) # CHANGE n TO 20

df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of main effect", var = "rateX2", xvar = "effectX2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-2.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX2,rateX2)  %>% group_by(design,family,effectX2) %>% mutate(rank = rank(rateX2))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshape_by_design(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of main effect", var = "rank", hovervar = "rateX2", xvar = "effectX2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-2.2").classList.add("hidden"); }); </script>

@@

::: {#fig-power-interaction}
<div id="plot-power-3.1">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
data <- read_data(prefix, alpha=.05, effectType = 5, distributions)

df <- reshape_by_design(data, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_error_by_design_2(df, xlab = "magnitude of interaction effect", var = "rateX1X2", xvar = "effectX1X2", max = 104,  ytitle = 'Power (%)')
```
</div>

<div id="plot-power-3.2">
```{r, echo=FALSE, fig.height=3.3, fig.width = 9, warning=FALSE}
df <- data %>% arrange(design,family,effectX1X2,rateX1X2)  %>% group_by(design,family,effectX1X2) %>% mutate(rank = rank(rateX1X2))
df <- as.data.frame(df) %>% reshape_by_design(dnames, effectvars = c("effectX1","effectX2","effectX1X2"))

#df <- reshape_by_design(df, dnames, effectvars = c("effectX1","effectX2","effectX1X2"))
plotly_power_by_design(df, xlab = "magnitude of interaction effect", var = "rank", hovervar = "rateX1X2", xvar = "effectX1X2", max = 4.2, ytitle = 'Power - ranking')
```
</div> <style> .hidden { display: none; } </style> <script> document.addEventListener("DOMContentLoaded", function() { document.getElementById("plot-power-3.2").classList.add("hidden"); }); </script>
